Modelling the emergence of whisker barrels

### 2020-06-30 paper/briefpaper/brief.tex
Less terse section on Fgf8 misexpression

% Miscellaneous changes
\newcommand{\cmnt}[1]{\textcolor{blue}{#1}}
% Justify gamma/interaction parameter choice. major point 1.
\newcommand{\MPone}[1]{\textcolor{revpink}{#1}}
% Blue changes are major point 2 (competition mechanism) and other, general
% uncategorised changes.
\newcommand{\MPtwo}[1]{\textcolor{revblue}{#1}}
% Parameter search. Major point 3
\newcommand{\MPthreePar}[1]{\textcolor{revbblack}{#1}}
% Sensitivity analysis. Major point 3
\newcommand{\MPthreeSens}[1]{\textcolor{revgblack}{#1}}
% Justify competition:
\newcommand{\mpfive}[1]{\textcolor{revpurp2}{#1}}
% Minor point 4:
\newcommand{\mpfour}[1]{\textcolor{revgreen}{#1}}
% Minor point 6:
\newcommand{\mpsix}[1]{\textcolor{revpurp}{#1}}
% Describe the metrics
\newcommand{\metrics}[1]{\textcolor{revred}{#1}}

@@

To further investigate the interplay of genetic and intrinsic mechanisms we
simulated a seminal barrel duplication experiment
\citep{shimogori_fibroblast_2005}, first by solving on a cortical domain
comprising two separate, identically shaped cortical boundaries. In this case
\cmnt{NOTE: The following only holds for the divisive normalization system -
  in the comp2 system, there's no `coupling' at all between the two regions,
  so the mirrored region arranges itself as expected with the one reversed
  guidance field.} one distinct cortical field per thalamic projection emerged, within one of the
two boundaries only, i.e., no duplication. However, merging the two fields to
create an extended mirror-symmetric boundary shape, with an anterior-posterior
guidance field reflected at the join, gave rise to two mirror-symmetrical
barrel fields comprising 2N barrels, i.e., two cortical fields for each
thalamic projection (Fig.\,\ref{fig:fgf8}). Together these results suggest that by the
misexpression of Fgf8, \cite{shimogori_fibroblast_2005}
effectively created one large barrel field rather than two distinct cortical
fields. \cmnt{Add something about the slightly off-vertical arrangement of the
  fields.}

@@

Add paragraph on whisker trimming here.

>>>>

% Miscellaneous changes
\newcommand{\cmnt}[1]{\textcolor{blue}{#1}}
% Justify gamma/interaction parameter choice. major point 1.
\newcommand{\MPone}[1]{\textcolor{revpink}{#1}}
% Blue changes are major point 2 (competition mechanism) and other, general
% uncategorised changes.
\newcommand{\MPtwo}[1]{\textcolor{revblue}{#1}}
% Parameter search. Major point 3
\newcommand{\MPthreePar}[1]{\textcolor{revbblack}{#1}}
% Sensitivity analysis. Major point 3
\newcommand{\MPthreeSens}[1]{\textcolor{revgblack}{#1}}
% More predictions. Major point 3
\newcommand{\MPthreePred}[1]{\textcolor{revorange}{#1}}
% Justify competition:
\newcommand{\mpfive}[1]{\textcolor{revpurp2}{#1}}
% Minor point 4:
\newcommand{\mpfour}[1]{\textcolor{revgreen}{#1}}
% Minor point 6:
\newcommand{\mpsix}[1]{\textcolor{revpurp}{#1}}
% Describe the metrics
\newcommand{\metrics}[1]{\textcolor{revred}{#1}}

@@

% This should be a little less terse than in the original.
\MPthreePred{To further investigate the interplay of genetic and intrinsic
  mechanisms we simulated two well known experimental manipulations of the
  whisker barrel system. First, we simulated a seminal barrel duplication
  experiments}
\citep{shimogori_fibroblast_2005,assimacopoulos_fibroblast_2012}
\MPthreePred{in which the growth factor Fgf8, which is normally expressed at
  the anterior end of the cortical sub-plate from around E9.5}
\citep{crossley_mouse_1995}, \MPthreePred{is ectopically expressed (by
  electroporation) also at the posterior end. Because Fgf8 sets off a chain of
  gene interactions which are involved in the control of the expression of
  ephrin and cadherin molecules in gradients across the cortical plate, its
  misexpression at the posterior pole of a cortical hemisphere could be
  expected to mirror those gradients which usually vary along the
  rostro-caudal axis. We assume that this results in a mirror of the primary
  barrel cortex boundary along the rostro-caudal axis, to match the
  experimental results of}
\citealp{assimacopoulos_fibroblast_2012}. \MPthreePred{We also assume that a
  further consequence of the posterior Fgf8 electroporation is the mirrored
  anterior-posterior guidance gradient $\rho_1$ (Fig.\,\ref{fig:fgf8}A). We
  mirrored this across a reflection line which is orthogonal to its angle
  $\phi_{\rho_1}=6$\textdegree, and left $\rho_2$ unmodified. Although the
  rostro-caudal boundary reflection is not perfectly aligned with $\rho_1$,
  and we might expect some modification of both $\rho_1$ \emph{and} $\rho_2$,
  mirroring only $\rho_1$ retains the simplicity of the guidance fields; they
  remain either linear ($\rho_2$), or piece-wise linear ($\rho_1$).}

\MPthreePred{The new boundary shape and $\rho_1$ guidance gradient were the
  only changes made to the simulation of Fig.\,\ref{fig:main}; the simulation
  was run with $N=41$ thalamocortical axon types as before and the initial
  values for $a_i$ were randomly initialised according to the same
  distribution. The result, after 30000 simulation steps, was two
  mirror-symmetrical barrel fields comprising $2N$ barrels
  (Fig\,\ref{fig:main}B). This result suggests that by the misexpression of
  Fgf8,} \cite{shimogori_fibroblast_2005} and \cite{assimacopoulos_fibroblast_2012}
  \MPthreePred{created the correct cortical
  conditions for the self-organization of the two mirrored barrel fields. }

%However, merging the two fields to
%create an extended mirror-symmetric boundary shape, with an anterior-posterior
%guidance field reflected at the join, gave rise to two mirror-symmetrical
%barrel fields comprising 2N barrels, i.e., two cortical fields for each
%thalamic projection (Fig.\,\ref{fig:fgf8}). Together these results suggest that by the
%misexpression of Fgf8, \cite{shimogori_fibroblast_2005}
%effectively created one large barrel field rather than two distinct cortical
%fields.

@@

\MPthreePred{Add paragraph on whisker trimming here.}
